### 2016-06-28 Docs/getting_started/getting_started.tex
update location of boxlib
update getting started with info of Microphysics

\item {\em Get a copy of \boxlib}.

\maestro\ requires the \boxlib\ library to manage the grids and 
parallelization.  We also rely on the build system in \boxlib\ to
build a \maestro\ executable.  \boxlib\ can be obtained via {\tt
git} as:
\begin{verbatim}
git clone https://ccse.lbl.gov/pub/Downloads/BoxLib.git
\end{verbatim}

@@

\maestro\ needs to know where to find \boxlib\, by specifying the 
{\tt BOXLIB\_HOME} environment variable.

If your shell is {\tt Bash}, add
\begin{verbatim}
export BOXLIB_HOME="/path/to/BoxLib/"
\end{verbatim}
to your {\tt .bashrc}.

If your shell is {\tt Csh/Tcsh}, add
\begin{verbatim}
setenv BOXLIB_HOME /path/to/BoxLib/
\end{verbatim}
to your {\tt .cshrc}.

Note: you must specify the full path to the BoxLib directory.  Do not
use ``$\sim$'' to refer to your home directory---the scripts used by
the build system will not be able to process this.

>>>>

\item {\em Get a copy of \microphysics}.

  \maestro\ and its compressible counterpart \castro\ share a
  common-set of microphysics solvers (nuclear reaction networks and
  equations of state).  These are kept in a separate repo.
  \microphysics\ is also available on github and can be obtained 
  via:
  \begin{verbatim}
git clone https://github.com/BoxLib-Codes/Microphysics.git
  \end{verbatim}

  You will periodic want to update \microphysics\ by doing
  \begin{verbatim}
git pull
  \end{verbatim}
  in the {\tt Microphysics/} directory
.
\item {\em Get a copy of \boxlib}.

  \maestro\ requires the \boxlib\ library to manage the grids and
  parallelization.  We also rely on the build system in \boxlib\ to
  build a \maestro\ executable.  \boxlib\ is also available on github
  and can be obtained via:
  \begin{verbatim}
git clone https://github.com/BoxLib-Codes/BoxLib.git
  \end{verbatim}

@@

  \maestro\ needs to know where to find \boxlib, by specifying the
  {\tt BOXLIB\_HOME} environment variable, and where
  to find \microphysics, bt specifying the {\tt
  MICROPHYSICS\_HOME} environment variable.

  If your shell is {\tt Bash}, add
  \begin{verbatim}
export BOXLIB_HOME="/path/to/BoxLib/"
export MICROPHYSICS_HOME="/path/to/Microphysics/"
  \end{verbatim}
  to your {\tt .bashrc}.

  If your shell is {\tt Csh/Tcsh}, add
  \begin{verbatim}
setenv BOXLIB_HOME /path/to/BoxLib/
setenv MICROPHYSICS_HOME /path/to/Microphysics/
  \end{verbatim}
  to your {\tt .cshrc}.

  Note: you must specify the full path to the {\tt BoxLib/} and {\tt
    Microphysics/} directory.  Do not use ``$\sim$'' to refer to your
  home directory---the scripts used by the build system will not be
  able to process this.
